### 2015-01-14 fundamentals/impl.tex

\Cyclus provides a novel representation of entities in the nuclear fuel cycle 
that reflects the reality in international nuclear power: production
encompassing facilities, institutions managing those facilities, and regions. While
some simulators \cite{adrianova_desae_2008} have provided a notion of static regional
effects, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through the
parent-child hierarchy described in \S \ref{sec:interchangeability}, where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

>>>>

\Cyclus provides a novel representation of entities in the nuclear fuel cycle 
that reflects the reality in international nuclear power: production
encompassing facilities, institutions managing those facilities, and regions. While
some simulators \cite{andrianova_desae_2008} have provided a notion of static regional
effects, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through the
parent-child hierarchy described in \S \ref{sec:interchangeability}, where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

### 2015-01-14 fundamentals/intro.tex

\Cyclus, therefore, is a dynamic, agent-based model, which employs a modular 
architecture, an open development process, discrete agents, discrete time, and 
arbitrarily detailed isotopic resolution of materials.  Dynamic nuclear fuel 
cycle analysis more realistically supports a range of simulation goals than 
static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
allows cross-institutional collaboration, increases code robustness, and 
cultivates an ecosystem of modeling and calculation options 
\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
nuclear fuel cycle simulator capture these modern insights so that challenges 
in nuclear fuel cycle analysis can be better addressed.

@@

\Cyclus emerged from a line of tools seeking to break this practice. 
Its precurser,
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, began
at \gls{LDRD} within \gls{INL} and sought 
to provide generic regional capability.  Based on lessons learned from 
Version 1, the 
\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
provide more generality and an extensible interface to facilitate 
collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2} 
effort by implementing increased modularity and encapsulation.  The result is  
a dynamic simulator that treats both materials and facilities discretely, with 
an architecture that permits simulations with multiple and variable levels of 
fidelity. The simulator's agent-based framework for tracking the 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing fuel cycle simulators.

>>>>

\Cyclus, therefore, is a dynamic, agent-based model, which employs a modular 
architecture, an open development process, discrete agents, discrete time, and 
arbitrarily detailed isotopic resolution of materials.  Dynamic nuclear fuel 
cycle analysis more realistically supports a range of simulation goals than 
static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
allows cross-institutional collaboration, increases code robustness \cite{cohen_modern_2010}, and 
cultivates an ecosystem of modeling and calculation options.  The fundamental concepts of the \Cyclus 
nuclear fuel cycle simulator capture these modern insights so that challenges 
in nuclear fuel cycle analysis can be better addressed.

@@

\Cyclus emerged from a line of tools seeking to break this practice.  
Its precursor,
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, began
as an \gls{LDRD} project within \gls{INL} and sought 
\gls{ORION}\cite{}, and 
to provide generic regional capability.  Based on lessons learned from 
Version 1, the 
\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
provide more generality and an extensible interface to facilitate 
collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2} 
effort by implementing increased modularity and encapsulation.  The result is  
a dynamic simulator that treats both materials and facilities discretely, with 
an architecture that permits simulations with multiple and variable levels of 
fidelity. The simulator's agent-based framework for tracking the 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing fuel cycle simulators.
